Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-20 paper.tex
update

\textbf{Definition 1.} A request from users is defined as a composition task in a tuple: $Comp.T = \{I_{T}, O_{T}\}$ by giving a set of task inputs $I_{T}$ and expecting  a set of desired task outputs $O_{T}$, where $I_{T}$ and $O_{T}$ are associated with related concepts $I^{C}_{T}$ and $O^{C}_{T}$ respectively in an ontology $O = \{C, Taxonomy \mid I^{C}_{T}, O^{C}_{T}  \subseteq C \}$.

@@

\textbf{Definition 4.} Given $(a \in O^{C}_{S_m}) \vee (b \in I^{C}_{S_n}) \wedge (m \neq n) $, a $full match(a \rightarrow b)$ holds if $type(a, b)$ returns $exact$ or $plugin$. The operator ``$ \rightarrow$'' means $a$ is passed to $b$, and $b$ is fully satisfied by $a$. The full match is a guarantee of completely valid  ``$ \rightarrow$'' operation, whereas, partial matches are not considered in this paper.
\vspace{0.3cm}

@@

$e = \{ (O_{S_{src}} \cup I_{S_{src}}) \mid \forall o \in O_{S_{src}}, \exists i \in O_{S_{src}} \wedge fullmatch (o \rightarrow i) \}$
\vspace{0.5cm}

@@

\textbf{Definition 5.} $V_{A}(WG)$ is a function that given a $WG$, a aggregated $availability$ value is returned, which is defined as :
$V_{A}(WG)=\prod\limits^n_{k=1}a_k$, for all ${S_1, S_2, ... S_n} \subset V$.

\textbf{Definition 6.} $V_{R}(WG)$ is a function that given a $WG$, a aggregated $reliability$ value is returned, which is defined as :
$V_{R}(WG)=\prod\limits^n_{k=1}r_k$, for all ${S_1, S_2, ... S_n} \subset V$.

\textbf{Definition 7.} $V_{C}(WG)$ is a function that given a $WG$, a aggregated cost value is returned, which is defined as :
$V_{C}(WG)=\sum\limits^n_{k=1}c_k$, for all ${S_1, S_2, ... S_n} \subset V$.

\textbf{Definition 8.} $V_{T}(WG)$ is a function that given a $WG$, a aggregated time value is returned, where  $T$ is determined by the most time-consuming path in the composition flow of the solution, which is defined as :
$V_{T}(WG)$ $=MAX\{timePath(WG)_n$ $|n\in\{1,\ldots,m\}\}$, where m is the number of $timePath$.

@@

\textbf{Composition Problem}
A set of semantic web services $S$ are chained as a weighted DAG composition mode $WG$ when a composition task $Comp.T$ is requested by users. The composition problem considered in this paper satisfying the follows:

>>>>

\textbf{Definition 1.} A request from users is defined as a composition task in a tuple: $Comp.T = \{I_{T}, O_{T}\}$ by giving a set of task inputs $I_{T}$ and expecting  a set of desired task outputs $O_{T}$, where $I_{T}$ and $O_{T}$ are associated with related concepts $I^{C}_{T}$ and $O^{C}_{T}$ respectively in an ontology $O = \{(C, Taxonomy) \mid I^{C}_{T}, O^{C}_{T}  \subseteq C \}$.

@@

\textbf{Definition 4.} Given $(a \in O^{C}_{S_m}) \vee (b \in I^{C}_{S_n}) \wedge (m \neq n) $, a $full match(a \Rightarrow b)$ holds if $type(a, b)$ returns $exact$ or $plugin$. The operator ``$ \Rightarrow$'' means $a$ is passed to $b$, and $b$ is fully satisfied by $a$. The full match is a guarantee of completely valid  ``$ \Rightarrow$'' operation, whereas, partial matches are not considered in this paper.

\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $q(a \Rightarrow b)$ is a function that given a output-related concept of a service and a input-related concept of another service, it returns the concept similarities between them.
\vspace{0.3cm}

@@

$e = \{ (O_{S_{src}} \cup I_{S_{src}}) \mid \forall o \in O_{S_{src}}, \exists i \in O_{S_{src}} \wedge fullmatch (o \Rightarrow i) \}$
\vspace{0.5cm}

@@

\textbf{Definition 6.} $V_{A}(WG)$ is a function that given a $WG$, a aggregated $availability$ value is returned, which is defined as :
$V_{A}(WG)=\prod\limits^n_{k=1}a_k$, for all ${S_1, S_2, ... S_n} \subset V$.

\textbf{Definition 7.} $V_{R}(WG)$ is a function that given a $WG$, a aggregated $reliability$ value is returned, which is defined as :
$V_{R}(WG)=\prod\limits^n_{k=1}r_k$, for all ${S_1, S_2, ... S_n} \subset V$.

\textbf{Definition 8.} $V_{C}(WG)$ is a function that given a $WG$, a aggregated cost value is returned, which is defined as :
$V_{C}(WG)=\sum\limits^n_{k=1}c_k$, for all ${S_1, S_2, ... S_n} \subset V$.

\textbf{Definition 9.} $V_{T}(WG)$ is a function that given a $WG$, a aggregated time value is returned, where  $T$ is determined by the most time-consuming path in the composition flow of the solution, which is defined as :
$V_{T}(WG)$ $=MAX\{timePath(WG)_n$ $|n\in\{1,\ldots,m\}\}$, where m is the number of $timePath$.

@@

\textbf{Composition Problem}
A set of semantic web services $S$ are chained as a weighted DAG composition mode $WG$ when a composition task $Comp.T$ is requested by users. The composition problem considered in this paper to automatically generate $WG$, satisfying the follows:

$\forall WG^{'}$ , $q(a \Rightarrow b) \cup V_{A}(WG^{'}) \cup V_{R}(WG^{'}) \cup V_{C}(WG^{'}) \cup V_{T}(WG^{'})  \leq q(a \Rightarrow b) \cup V_{A}(WG) \cup V_{R}(WG) \cup V_{C}(WG) \cup V_{T}(WG) $
